An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-08-12 neurips-19/response/neurips_2019_author_response.tex
Added comments from MB

>>>>

\hline
In response to Blanschko:
Noted the paper \url{https://arxiv.org/pdf/1905.12511.pdf} that we didn't cite.

He also mentions that consistency sometimes unnecessarily hinders us, and points us to \url{https://pdfs.semanticscholar.org/3a0d/b4d2ee997c1de2642a607b4f963b1f9468f5.pdf} for one example.
